\documentclass[a1paper,25pt]{article}
\usepackage[paper=a1paper,landscape=false,margin=2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{graphicx,ifthen,color,pgf,multicol,calc}
\usepackage{amsmath,amssymb,booktabs}
\usepackage[charter]{mathdesign}
\usepackage[sfdefault]{noto}
\usepackage[english]{babel}
\usepackage{tikz}

\pagestyle{empty}
\setlength{\columnsep}{2cm}

% TU/e colors
\definecolor{tuescarlet}{RGB}{200,24,24}
\definecolor{tuedarkblue}{RGB}{16,16,115}

% Custom title
\newcommand{\postertitle}[4]{%
\begin{tikzpicture}[remember picture,overlay]
\fill[tuescarlet] (current page.north west) rectangle ([yshift=-12cm]current page.north east);
\node[anchor=north west, white, font=\fontsize{60}{72}\selectfont\bfseries] at ([xshift=3cm,yshift=-3cm]current page.north west) {#1};
\node[anchor=north west, white, font=\fontsize{36}{44}\selectfont] at ([xshift=3cm,yshift=-6.5cm]current page.north west) {#2};
\node[anchor=north west, white, font=\fontsize{28}{34}\selectfont] at ([xshift=3cm,yshift=-9cm]current page.north west) {#3};
\node[anchor=south west, black, font=\fontsize{20}{24}\selectfont\bfseries] at ([xshift=3cm,yshift=1.5cm]current page.south west) {#4};
\end{tikzpicture}
}

\begin{document}
\postertitle{MedGemma vs BiomedCLIP for Melanoma Classification}{A Comparative Study on Vision-Language Models in Medical Imaging}{Team 5}{Department of Biomedical Engineering}

\vspace*{10cm}

\begin{multicols}{3}

\section*{\fontsize{40}{48}\selectfont Abstract}
\fontsize{24}{30}\selectfont
We compare MedGemma (medical vision-language model) and BiomedCLIP (visual embeddings + classifiers) for melanoma vs nevus classification on 920 histopathology images from Open-MELON.

\textbf{Key finding:} MedGemma's 68\% accuracy drops to 53\% (random chance) when classes are balanced. BiomedCLIP maintains 73\% regardless of balance.

\vspace{1cm}
\section*{\fontsize{40}{48}\selectfont Methodology}
\fontsize{24}{30}\selectfont

\textbf{Dataset:} Open-MELON-VL-2.5K\\
920 melanoma/nevus cases (618 melanoma, 302 nevus)

\textbf{MedGemma:} Generate captions $\rightarrow$ Extract diagnosis via keywords $\rightarrow$ RAGAS evaluation

\textbf{BiomedCLIP:} Extract 512-dim embeddings $\rightarrow$ Zero-shot or supervised classifiers

\textbf{Balanced Evaluation:} Equal sampling from each class, averaged over 10 trials

\vspace{1cm}
\section*{\fontsize{40}{48}\selectfont Results}
\fontsize{24}{30}\selectfont

\textbf{Accuracy (Original vs Balanced):}
\vspace{0.5cm}

{\fontsize{22}{28}\selectfont
\begin{tabular}{lcc}
\toprule
\textbf{Model} & \textbf{Original} & \textbf{Balanced} \\
\midrule
MedGemma & 68.4\% & \textbf{53.2\%} \\
BiomedCLIP + RF & 73.9\% & \textbf{73.2\%} \\
BiomedCLIP + SVM & 71.2\% & \textbf{73.6\%} \\
\bottomrule
\end{tabular}
}

\vspace{1cm}
\textbf{MedGemma Diagnosis:}
\vspace{0.5cm}

{\fontsize{22}{28}\selectfont
\begin{tabular}{lc}
\toprule
\textbf{Metric} & \textbf{Value} \\
\midrule
Melanoma correctly ID'd & 99.4\% \\
Nevus correctly ID'd & \textbf{0.7\%} \\
Hallucinated diagnoses & 83\% \\
\bottomrule
\end{tabular}
}

\vspace{0.5cm}
MedGemma hallucinated ``lymphoma'' (292 cases) and ``carcinoma'' (196 cases).

\columnbreak

\section*{\fontsize{40}{48}\selectfont Failure Analysis}
\fontsize{24}{30}\selectfont

\textbf{BiomedCLIP failures} are interpretable:
\begin{itemize}
\item Atypical nevi misclassified as melanoma
\item Spindle cell nevi look similar to melanoma
\item In-situ melanomas lack invasive features
\end{itemize}

\textbf{MedGemma failures} are systemic:
\begin{itemize}
\item Defaults to ``melanoma'' regardless of content
\item No ability to distinguish visual features
\item Only 2/302 nevus samples correctly identified
\end{itemize}

\vspace{1cm}
\section*{\fontsize{40}{48}\selectfont Critical Discussion}
\fontsize{24}{30}\selectfont

\textbf{Why MedGemma fails:}
\begin{itemize}
\item Insufficient melanoma/nevus training data
\item Captioning $\neq$ classification objective
\item 4B model too small for medical reasoning
\end{itemize}

\textbf{Why BiomedCLIP succeeds:}
\begin{itemize}
\item Contrastive training on 15M medical pairs
\item Embeddings for semantic discrimination
\item Supervised classifier learns decision boundary
\end{itemize}

\columnbreak

\section*{\fontsize{40}{48}\selectfont Conclusion}
\fontsize{24}{30}\selectfont

\textbf{MedGemma provides no diagnostic value} for melanoma classification:
\begin{itemize}
\item Apparent accuracy is artifact of class imbalance
\item Hallucinates diagnoses in 83\% of cases
\item Correctly identifies only 0.7\% of nevus
\end{itemize}

\textbf{BiomedCLIP achieves genuine 73\% accuracy} that holds under balanced evaluation.

\vspace{0.5cm}
\fbox{\parbox{0.9\linewidth}{\centering\fontsize{28}{34}\selectfont\bfseries
For medical image classification,\\embedding-based approaches outperform\\caption-based VLMs.
}}

\vspace{1cm}
\section*{\fontsize{40}{48}\selectfont References}
\fontsize{20}{26}\selectfont

[1] Google (2024). MedGemma: Open Medical AI Models.

[2] Zhang et al. (2023). BiomedCLIP: A Multimodal Biomedical Foundation Model.

[3] Han et al. (2024). Open-MELON-VL-2.5K Dataset.

[4] Es et al. (2023). RAGAS: Automated Evaluation. arXiv:2309.15217.

\end{multicols}
\end{document}
